An equivalence of compositional frameworks

### 2018-09-30 EquivCompFrameworks_20180911kc.tex
even more diagram condensing

\node (B) at (1,1) {$d$};

@@

(A) edge node[left]{$i$} (B)
(C) edge node[right]{$o$} (B);

@@

\node (B) at (1,1) {$R(d)$};

@@

\node (D) at (3,0.5) {$d \in F(R(d))$};
(A) edge node[left]{$R(i) {\eta_c}$} (B)
(C) edge node[right]{$R(o) {\eta_{c^\prime}}$} (B);

@@

(A) edge node[left]{$i^\prime$} (B)
(C) edge node[right]{$o^\prime$} (B);

@@

Next we show that the double functor $\mathbb{E}$ is strong by exhibiting natural isomorphisms $$\mathbb{E}_{M,N} \colon \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N)$$ for every pair of composable horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\bold{D})$ and for each object $c \in { _L \mathbb{C}\textnormal{sp}(\bold{D})}$ a natural isomorphism $$\mathbb{E}_c \colon \hat{U}_{\mathbb{E}(c)} \xrightarrow{\sim} \mathbb{E}(U_c)$$ where $U$ and $\hat{U}$ are the unit structure functors of $_L \mathbb{C} \textnormal{sp}(\bold{D})$ and $\mathbb{F}\textnormal{Cospan}(\bold{C})$, respectively. For any object $c$, the horizontal 1-cell $\hat{U}_{\mathbb{E}(c)}$ is given by $\hat{U}_c$ which is given by the pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c$};
\node (B) at (1,1) {$c$};
\node (C) at (2,0) {$c$};
\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1$} (B)
(C) edge node[right]{$1$} (B);
\end{tikzpicture}
\]
The horizontal 1-cell $U_c$ is given by
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c)$};
\node (B) at (1,1) {$L(c)$};
\node (C) at (2,0) {$L(c)$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1$} (B)
(C) edge node[right]{$1$} (B);
\end{tikzpicture}
\]
and so $\mathbb{E}(U_c)$ is given by the pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c$};
\node (B) at (1,1) {$R(L(c))$};
\node (C) at (2,0) {$c$};
\node (D) at (3.25,0.5) {$!_c \in F(R(L(c)))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\eta_c$} (B)
(C) edge node[right]{$\eta_c$} (B);
\end{tikzpicture}
\]
Then we can obtain the natural isomorphism $\mathbb{E}_c$ as the 2-morphism
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$c$};
\node (A') at (0,-1) {$c$};
\node (B') at (1,-1) {$R(L(c))$};
\node (C') at (2,-1) {$c$};
\node (D) at (3,0) {$!_c \in F(c)$};
\node (D') at (3.25,-1) {$!_c \in F(R(L(c)))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B)
(A') edge node[above]{$\eta_c$} (B')
(C') edge node[above]{$\eta_c$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{$\eta_c$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]
$$\iota \colon F(\eta_c)(!_c) \xrightarrow{!} L(c)$$
of $\mathbb{F}\textnormal{Cospan}(\bold{C})$. Seems reasonable...

@@

\node (E) at (4,1) {$d^\prime$};

@@

(A) edge node[left]{$i$} (B)
(C) edge node[right]{$o$} (B)
(D) edge node[left]{$i^\prime$} (E)
(F) edge node[right]{$o^\prime$} (E);

@@

\node (E) at (4,1) {$R(d^\prime)$};

@@

(A) edge node[left]{$R(i) \eta_{c_1}$} (B)
(C) edge node[right]{$R(o) \eta_{c_2}$} (B)
(D) edge node[left]{$R(i^\prime) \eta_{c_2}$} (E)
(F) edge node[right]{$R(o^\prime) \eta_{c_3}$} (E);

@@

\node (B) at (1,1) {$R(d)+_{c_2}R(d^\prime)$};
\node (G) at (1,-0.5) {$\hat{d} \in F(R(d)+_{c_2}R(d^\prime))$};

@@

(A) edge node[left]{$j \psi R(i) \eta_{c_1}$} (B)
(C) edge node[right]{$j \psi R(o^\prime) \eta_{c_3}$} (B);

@@

\node (B) at (1,1) {$d+_{L(c_2)}d^\prime$};
\node (C) at (2,0) {$L(c_3)$};

@@

(A) edge node[left]{$J \zeta i$} (B)
(C) edge node[right]{$J \zeta o^\prime$} (B);

@@

\node (B) at (1,1) {$R(d+_{L(c_2)}d^\prime)$};
\node (G) at (1,-0.5) {$d+_{L(c_2)} d^\prime \in F(R(d+_{L(c_2)}d^\prime))$};

@@

(A) edge node[left]{$R(J \zeta i) \eta_{c_1}$} (B)
(C) edge node[right]{$R(J \zeta o^\prime) \eta_{c_3}$} (B);

@@

For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \colon U_{1_{\mathbb{F}\textnormal{Cospan}(\bold{C})}} \to \mathbb{E}(U_{1_{_L \mathbb{C}\textnormal{sp}(\bold{D})}})$ where the horizontal 1-cell $U_{1_{\mathbb{F}\textnormal{Cospan}(\bold{C})}}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_\bold{C}$};
\node (B) at (1,1) {$1_\bold{C}$};
\node (C) at (2,0) {$1_\bold{C}$};
\node (D) at (3,0.5) {$!_{1_{\bold{C}}} \in F(1_\bold{C})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1$} (B)
(C) edge node[right]{$1$} (B);
\end{tikzpicture}
\]
where $!_{1_{\bold{C}}} = \phi \colon \bold{1} \to F(1_\bold{C})$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$. The horizontal 1-cell $U_{1_{_L \mathbb{C}\textnormal{sp}(\bold{D})}}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(1_\bold{C})$};
\node (B) at (1,1) {$L(1_\bold{C})$};
\node (C) at (2,0) {$L(1_\bold{C})$};
%\node (D) at (3,0.5) {$I \in F(1_\bold{C})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$1$} (B)
(C) edge node[right]{$1$} (B);
\end{tikzpicture}
\]
where here we make use of the fact that the left adjoint $L \colon (\bold{C},+,1_\bold{C}) \to (\bold{D},+,1_\bold{D})$ preserves all colimits and thus $L(1_\bold{C}) \cong 1_\bold{D}$. The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\bold{D})}})$ is given by the pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_\bold{C}$};
\node (B) at (1,1) {$R(L(1_\bold{C}))$};
\node (C) at (2,0) {$1_\bold{C}$};
\node (D) at (3.5,0.5) {$!_{1_\bold{C}} \in F(R(L(1_\bold{C}))) \cong F(1_\bold{C})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{${\eta_{1_\bold{C}}}$} (B)
(C) edge node[right]{${\eta_{1_\bold{C}}}$} (B);
\end{tikzpicture}
\]
The isomorphism $\delta$ is then given by the 2-morphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_\bold{C}$};
\node (B) at (1,0) {$1_{\bold{C}}$};
\node (C) at (2,0) {$1_\bold{C}$};
\node (A') at (0,-1) {$1_\bold{C}$};
\node (B') at (1,-1) {$R(L(1_\bold{C}))$};
\node (C') at (2,-1) {$1_\bold{C}$};
\node (D) at (3,0) {$!_{1_\bold{C}} \in F(1_\bold{C})$};
\node (D') at (3.75,-1) {$!_{1_\bold{C}} \in F(R(L(1_\bold{C}))) \cong F(1_\bold{C})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B)
(A') edge node[above]{${\eta_{1_\bold{C}}}$} (B')
(C') edge node[above]{${\eta_{1_\bold{C}}}$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{${\eta_{1_\bold{C}}}$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]
$$\iota_{{\eta_{1_\bold{C}}}} \colon F({\eta_{1_\bold{C}}}(!_{1_\bold{C}})) \to !_{1_\bold{C}}$$
of $\mathbb{F}\textnormal{Cospan}(\bold{C})$.

@@

(A) edge node[left]{$R(i) \eta_{c_1}$} (B)
(C) edge node[right]{$R(o) \eta_{c_2}$} (B)
(D) edge node[left]{$R(i^\prime) \eta_{c_1^\prime}$} (E)
(F) edge node[right]{$R(o^\prime) \eta_{c_2^\prime}$} (E);

@@

\node (B) at (1,1) {$R(d)+R(d^\prime)$};
\node (C) at (2,0) {$c_2+c_2^\prime$};
\node (D) at (1,-0.5) {$\hat{d} \in F(R(d)+R(d^\prime)$}; 

@@

(A) edge node[left]{$R(i) \eta_{c_1} +R(i^\prime) \eta_{c_1^\prime}$} (B)
(C) edge node[right]{$R(o) \eta_{c_2} + R(o) \eta_{c_2^\prime}$} (B);

@@

\node (B) at (1,1) {$d+d^\prime$};
\node (C) at (2,0) {$L(c_2+c_2^\prime)$};

@@

(A) edge node[left]{$i+i^\prime$} (B)
(C) edge node[right]{$o+o^\prime$} (B);

@@

\node (B) at (1,1) {$R(d+d^\prime)$};
\node (C) at (2,0) {$c_2+c_2^\prime$};
\node (D) at (1,-0.5) {$d+d^\prime \in F(R(d+d^\prime))$};

@@

(A) edge node[left]{$R(i+i^\prime) \eta_{c_1+c_1^\prime}$} (B)
(C) edge node[right]{$R(o+o^\prime) \eta_{c_2+c_2^\prime}$} (B);

@@

\node (B) at (1,1) {$d_1$};

@@

\node (E) at (4,1) {$d_2$};

@@

\node (H) at (7,1) {$d_3$};

@@

(A) edge node[left]{$i_1$} (B)
(C) edge node[right]{$o_1$} (B)
(D) edge node[left]{$i_2$} (E)
(F) edge node[right]{$o_2$} (E)
(G) edge node[left]{$i_3$} (H)
(I) edge node[right]{$o_3$} (H);

@@

			\node (d2) at (7.5,1.5) {$1_{\mathbb{F}\textnormal{Cospan}(\bold{C})} \otimes \mathbb{E}(M_1)$};
			\node (a2) at (-4,1.5) {$1_\bold{C}+c_1$};
			\node (b2) at (0.5,1.5) {$1_\bold{C}+R(d_1)$};
			\node (c2) at (5,1.5) {$1_\bold{C}+c_1^\prime$};
			\node (d3) at (7.5,3) {$\mathbb{E}(M_1)$};
                                \node (a3) at (-4,3) {$c_1$};
			\node (b3) at (0.5,3) {$R(d_1)$};
			\node (c3) at (5,3) {$c_1^\prime$};
			\node (d4) at (7.5,-1.5) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\bold{D})} \otimes M_1)$};
                                \node (a5) at (-4,-1.5) {$1_\bold{C}+c_1^\prime$};
			\node (b5) at (0.5,-1.5) {$R(L(1_\bold{C})+d_1)$};
			\node (c5) at (5,-1.5) {$1_\bold{C}+c_1^\prime$};
			\node (d5) at (7.5,-3) {$\mathbb{E}(M_1)$};
                                \node (a6) at (-4,-3) {$c_1$};
			\node (b6) at (0.5,-3) {$R(d_1)$};
			\node (c6) at (5,-3) {$c_1^\prime$};

@@

\node(d) at (1.5,10.5) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
\node (d2) at (1.5,12) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
\node (d3) at (1.5,13.5) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
\node (d4) at (1.5,15) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
\node (d5) at (1.5,9) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
\node (d6) at (1.5,7.5) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
\node (d7) at (1.5,6) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};

@@

			\node (a2) at (-4.25,1.5) {$(c_1+c_2)+c_3$};
			\node (b2) at (1.5,1.5) {$R(d_1+d_2)+R(d_3)$};
			\node (c2) at (7.25,1.5) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
                                \node (a3) at (-4.25,3) {$(c_1+c_2)+c_3$};
			\node (b3) at (1.5,3) {$R((d_1+d_2)+d_3)$};
			\node (c3) at (7.25,3) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
                                \node (a4) at (-4.25,4.5) {$c_1+(c_2+c_3)$};
			\node (b4) at (1.5,4.5) {$R(d_1+(d_2+d_3))$};
			\node (c4) at (7.25,4.5) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
                                \node (a5) at (-4.25,-1.5) {$c_1+(c_2+c_3)$};
			\node (b5) at (1.5,-1.5) {$R(d_1)+(R(d_2)+R(d_3))$};
			\node (c5) at (7.25,-1.5) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
                                \node (a6) at (-4.25,-3) {$c_1+(c_2+c_3)$};
			\node (b6) at (1.5,-3) {$R(d_1)+R(d_2+d_3)$};
			\node (c6) at (7.25,-3) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
                                \node (a7) at (-4.25,-4.5) {$c_1+(c_2+c_3)$};
			\node (b7) at (1.5,-4.5) {$R(d_1+(d_2+d_3))$};
			\node (c7) at (7.25,-4.5) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};

@@

\node (d2) at (7,1.5) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
\node (d3) at (7,3) {$\mathbb{E}(M_2 \otimes M_1)$};
\node (d4) at (7,-1.5) {$\mathbb{E}(M_1 \otimes M_2)$};
\node (d5) at (7,-3) {$\mathbb{E}(M_2 \otimes M_1)$};

@@

			\node (a2) at (-4,1.5) {$c_2+c_1$};
			\node (b2) at (0.5,1.5) {$R(d_2)+R(d_1)$};
			\node (c2) at (5,1.5) {$c_2^\prime+c_1^\prime$};
                                \node (a3) at (-4,3) {$c_2+c_1$};
			\node (b3) at (0.5,3) {$R(d_2+d_1)$};
			\node (c3) at (5,3) {$c_2^\prime + c_1^\prime$};
                                \node (a5) at (-4,-1.5) {$c_1+c_2$};
			\node (b5) at (0.5,-1.5) {$R(d_1+d_2)$};
			\node (c5) at (5,-1.5) {$c_1^\prime+c_2^\prime$};
                                \node (a6) at (-4,-3) {$c_2+c_1$};
			\node (b6) at (0.5,-3) {$R(d_2+d_1)$};
			\node (c6) at (5,-3) {$c_2^\prime + c_1^\prime$};

@@

(A) edge node[left]{$R(i)$} (B)
(C) edge node[right]{$R(o)$} (B);

@@

\node (B) at (1,1) {$d$};
(A) edge node[left]{$\tau_{R(d)}L(R(i))$} (B)
(C) edge node[right]{$\tau_{R(d)}L(R(o))$} (B);

@@

(A) edge node[left]{$I$} (B)
(C) edge node[right]{$O$} (B);

@@

(A) edge node[left]{$\tau_c L(I)$} (B)
(C) edge node[right]{$\tau_c L(O)$} (B);

@@

(A) edge node[left]{$R(\tau_c)I$} (B)
(C) edge node[right]{$R(\tau_c)O$} (B);

@@

\node (B) at (1,1) {$M$};

@@

\node (B) at (1,1) {$R(M)$};

@@

\node (D) at (3,0.5) {$M \in F(R(M))$};
(A) edge node[left]{$R(i)$} (B)
(C) edge node[right]{$R(o)$} (B);

@@

\node (B) at (1,1) {$N$};

@@

\node (D) at (3,0.5) {$M \in F(N)$};

@@

\node (E) at (4,1) {$M^\prime$};

@@

(A) edge node[left]{$i_1$} (B)
(C) edge node[right]{$o_1$} (B)
(D) edge node[left]{$i_2$} (E)
(F) edge node[right]{$o_2$} (E);

>>>>

@@

@@

@@

(A) edge node[above]{$R(i) {\eta_c}$} (B)
(C) edge node[above]{$R(o) {\eta_{c^\prime}}$} (B);

@@

@@

Next we show that the double functor $\mathbb{E}$ is strong by exhibiting natural isomorphisms $$\mathbb{E}_{M,N} \colon \mathbb{E}(M) \odot \mathbb{E}(N) \xrightarrow{\sim} \mathbb{E}(M \odot N)$$ for every pair of composable horizontal 1-cells $M$ and $N$ of $_L \mathbb{C}\textnormal{sp}(\bold{D})$ and for each object $c \in { _L \mathbb{C}\textnormal{sp}(\bold{D})}$ a natural isomorphism $$\mathbb{E}_c \colon \hat{U}_{\mathbb{E}(c)} \xrightarrow{\sim} \mathbb{E}(U_c)$$ where $U$ and $\hat{U}$ are the unit structure functors of $_L \mathbb{C} \textnormal{sp}(\bold{D})$ and $\mathbb{F}\textnormal{Cospan}(\bold{C})$, respectively. For any object $c$, the horizontal 1-cell $\hat{U}_{\mathbb{E}(c)}$ is given by $\hat{U}_c$ which is given by the pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$c$};
\node (D) at (3,0) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B);
\end{tikzpicture}
\]
The horizontal 1-cell $U_c$ is given by
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c)$};
\node (B) at (1,0) {$L(c)$};
\node (C) at (2,0) {$L(c)$};
%\node (D) at (3,0.5) {$!_c \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B);
\end{tikzpicture}
\]
and so $\mathbb{E}(U_c)$ is given by the pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c$};
\node (B) at (1,0) {$R(L(c))$};
\node (C) at (2,0) {$c$};
\node (D) at (3.25,0) {$!_c \in F(R(L(c)))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\eta_c$} (B)
(C) edge node[above]{$\eta_c$} (B);
\end{tikzpicture}
\]
Then we can obtain the natural isomorphism $\mathbb{E}_c$ as the 2-morphism
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$c$};
\node (A') at (0,-1) {$c$};
\node (B') at (1,-1) {$R(L(c))$};
\node (C') at (2,-1) {$c$};
\node (D) at (3,0) {$!_c \in F(c)$};
\node (D') at (3.25,-1) {$!_c \in F(R(L(c)))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B)
(A') edge node[above]{$\eta_c$} (B')
(C') edge node[above]{$\eta_c$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{$\eta_c$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]
$$\iota \colon F(\eta_c)(!_c) \xrightarrow{!} L(c)$$
of $\mathbb{F}\textnormal{Cospan}(\bold{C})$. Seems reasonable...

@@

\node (E) at (4,0) {$d^\prime$};

@@

@@

\node (E) at (4,0) {$R(d^\prime)$};

@@

(D) edge node[above]{$R(i^\prime) \eta_{c_2}$} (E)
(F) edge node[above]{$R(o^\prime) \eta_{c_3}$} (E);

@@

\node (G) at (1.5,-0.5) {$\hat{d} \in F(R(d)+_{c_2}R(d^\prime))$};

@@

(C) edge node[above]{$j \psi R(o^\prime) \eta_{c_3}$} (B);

@@

\node (B) at (1.25,0) {$d+_{L(c_2)}d^\prime$};
\node (C) at (2.5,0) {$L(c_3)$};

@@

(A) edge node[above]{$J \zeta i$} (B)
(C) edge node[above]{$J \zeta o^\prime$} (B);

@@

\node (B) at (1.5,0) {$R(d+_{L(c_2)}d^\prime)$};
\node (G) at (1.5,-0.5) {$d+_{L(c_2)} d^\prime \in F(R(d+_{L(c_2)}d^\prime))$};

@@

(A) edge node[above]{$R(J \zeta i) \eta_{c_1}$} (B)
(C) edge node[above]{$R(J \zeta o^\prime) \eta_{c_3}$} (B);

@@

For the arrow component $\mathbb{E}_1$, we have an isomorphism $\delta \colon U_{1_{\mathbb{F}\textnormal{Cospan}(\bold{C})}} \to \mathbb{E}(U_{1_{_L \mathbb{C}\textnormal{sp}(\bold{D})}})$ where the horizontal 1-cell $U_{1_{\mathbb{F}\textnormal{Cospan}(\bold{C})}}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_\bold{C}$};
\node (B) at (1,0) {$1_\bold{C}$};
\node (C) at (2,0) {$1_\bold{C}$};
\node (D) at (3,0) {$!_{1_{\bold{C}}} \in F(1_\bold{C})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B);
\end{tikzpicture}
\]
where $!_{1_{\bold{C}}} = \phi \colon \bold{1} \to F(1_\bold{C})$ is the trivial decoration which comes from the structure of the symmetric lax monoidal pseudofunctor $F \colon \bold{C} \to \bold{Cat}$. The horizontal 1-cell $U_{1_{_L \mathbb{C}\textnormal{sp}(\bold{D})}}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(1_\bold{C})$};
\node (B) at (1,0) {$L(1_\bold{C})$};
\node (C) at (2,0) {$L(1_\bold{C})$};
%\node (D) at (3,0.5) {$I \in F(1_\bold{C})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B);
\end{tikzpicture}
\]
where here we make use of the fact that the left adjoint $L \colon (\bold{C},+,1_\bold{C}) \to (\bold{D},+,1_\bold{D})$ preserves all colimits and thus $L(1_\bold{C}) \cong 1_\bold{D}$. The horizontal 1-cell $\mathbb{E}(U_{1_{_L \mathbb{C} \textnormal{sp}(\bold{D})}})$ is given by the pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_\bold{C}$};
\node (B) at (1.25,0) {$R(L(1_\bold{C}))$};
\node (C) at (2.5,0) {$1_\bold{C}$};
\node (D) at (4,0) {$!_{1_\bold{C}} \in F(R(L(1_\bold{C}))) \cong F(1_\bold{C})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{${\eta_{1_\bold{C}}}$} (B)
(C) edge node[above]{${\eta_{1_\bold{C}}}$} (B);
\end{tikzpicture}
\]
The isomorphism $\delta$ is then given by the 2-morphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_\bold{C}$};
\node (B) at (1,0) {$1_{\bold{C}}$};
\node (C) at (2,0) {$1_\bold{C}$};
\node (A') at (0,-1) {$1_\bold{C}$};
\node (B') at (1,-1) {$R(L(1_\bold{C}))$};
\node (C') at (2,-1) {$1_\bold{C}$};
\node (D) at (3,0) {$!_{1_\bold{C}} \in F(1_\bold{C})$};
\node (D') at (3.75,-1) {$!_{1_\bold{C}} \in F(R(L(1_\bold{C}))) \cong F(1_\bold{C})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B)
(A') edge node[above]{${\eta_{1_\bold{C}}}$} (B')
(C') edge node[above]{${\eta_{1_\bold{C}}}$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{${\eta_{1_\bold{C}}}$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]
$$\iota_{{\eta_{1_\bold{C}}}} \colon F({\eta_{1_\bold{C}}}(!_{1_\bold{C}})) \to !_{1_\bold{C}}$$
of $\mathbb{F}\textnormal{Cospan}(\bold{C})$.

@@

(D) edge node[above]{$R(i^\prime) \eta_{c_1^\prime}$} (E)
(F) edge node[above]{$R(o^\prime) \eta_{c_2^\prime}$} (E);

@@

\node (B) at (2.25,0) {$R(d)+R(d^\prime)$};
\node (C) at (4.5,0) {$c_2+c_2^\prime$};
\node (D) at (2.25,-0.5) {$\hat{d} \in F(R(d)+R(d^\prime)$}; 

@@

(A) edge node[above]{$R(i) \eta_{c_1} +R(i^\prime) \eta_{c_1^\prime}$} (B)
(C) edge node[above]{$R(o) \eta_{c_2} + R(o) \eta_{c_2^\prime}$} (B);

@@

\node (B) at (1.5,0) {$d+d^\prime$};
\node (C) at (3,0) {$L(c_2+c_2^\prime)$};

@@

(A) edge node[above]{$i+i^\prime$} (B)
(C) edge node[above]{$o+o^\prime$} (B);

@@

\node (B) at (2,0) {$R(d+d^\prime)$};
\node (D) at (2,-0.5) {$d+d^\prime \in F(R(d+d^\prime))$};

@@

(A) edge node[above]{$R(i+i^\prime) \eta_{c_1+c_1^\prime}$} (B)
(C) edge node[above]{$R(o+o^\prime) \eta_{c_2+c_2^\prime}$} (B);

@@

\node (B) at (1,0) {$d_1$};

@@

\node (E) at (4,0) {$d_2$};

@@

\node (H) at (7,0) {$d_3$};

@@

(D) edge node[above]{$i_2$} (E)
(F) edge node[above]{$o_2$} (E)
(G) edge node[above]{$i_3$} (H)
(I) edge node[above]{$o_3$} (H);

@@

			\node (d2) at (7.5,1) {$1_{\mathbb{F}\textnormal{Cospan}(\bold{C})} \otimes \mathbb{E}(M_1)$};
			\node (a2) at (-4,1) {$1_\bold{C}+c_1$};
			\node (b2) at (0.5,1) {$1_\bold{C}+R(d_1)$};
			\node (c2) at (5,1) {$1_\bold{C}+c_1^\prime$};
			\node (d3) at (7.5,2) {$\mathbb{E}(M_1)$};
                                \node (a3) at (-4,2) {$c_1$};
			\node (b3) at (0.5,2) {$R(d_1)$};
			\node (c3) at (5,2) {$c_1^\prime$};
			\node (d4) at (7.5,-1) {$\mathbb{E}(1_{ _L \mathbb{C}\textnormal{sp}(\bold{D})} \otimes M_1)$};
                                \node (a5) at (-4,-1) {$1_\bold{C}+c_1^\prime$};
			\node (b5) at (0.5,-1) {$R(L(1_\bold{C})+d_1)$};
			\node (c5) at (5,-1) {$1_\bold{C}+c_1^\prime$};
			\node (d5) at (7.5,-2) {$\mathbb{E}(M_1)$};
                                \node (a6) at (-4,-2) {$c_1$};
			\node (b6) at (0.5,-2) {$R(d_1)$};
			\node (c6) at (5,-2) {$c_1^\prime$};

@@

\node(d) at (1.5,7) {$(\mathbb{E}(M_1) \otimes \mathbb{E}(M_2)) \otimes \mathbb{E}(M_3)$};
\node (d2) at (1.5,8) {$\mathbb{E}(M_1 \otimes M_2) \otimes \mathbb{E}(M_3)$};
\node (d3) at (1.5,9) {$\mathbb{E}((M_1 \otimes M_2) \otimes M_3)$};
\node (d4) at (1.5,10) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};
\node (d5) at (1.5,6) {$\mathbb{E}(M_1) \otimes (\mathbb{E}(M_2) \otimes \mathbb{E}(M_3))$};
\node (d6) at (1.5,5) {$\mathbb{E}(M_1) \otimes \mathbb{E}(M_2 \otimes M_3)$};
\node (d7) at (1.5,4) {$\mathbb{E}(M_1 \otimes (M_2 \otimes M_3))$};

@@

			\node (a2) at (-4.25,1) {$(c_1+c_2)+c_3$};
			\node (b2) at (1.5,1) {$R(d_1+d_2)+R(d_3)$};
			\node (c2) at (7.25,1) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
                                \node (a3) at (-4.25,2) {$(c_1+c_2)+c_3$};
			\node (b3) at (1.5,2) {$R((d_1+d_2)+d_3)$};
			\node (c3) at (7.25,2) {$(c_1^\prime+c_2^\prime)+c_3^\prime$};
                                \node (a4) at (-4.25,3) {$c_1+(c_2+c_3)$};
			\node (b4) at (1.5,3) {$R(d_1+(d_2+d_3))$};
			\node (c4) at (7.25,3) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
                                \node (a5) at (-4.25,-1) {$c_1+(c_2+c_3)$};
			\node (b5) at (1.5,-1) {$R(d_1)+(R(d_2)+R(d_3))$};
			\node (c5) at (7.25,-1) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
                                \node (a6) at (-4.25,-2) {$c_1+(c_2+c_3)$};
			\node (b6) at (1.5,-2) {$R(d_1)+R(d_2+d_3)$};
			\node (c6) at (7.25,-2) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};
                                \node (a7) at (-4.25,-3) {$c_1+(c_2+c_3)$};
			\node (b7) at (1.5,-3) {$R(d_1+(d_2+d_3))$};
			\node (c7) at (7.25,-3) {$c_1^\prime + (c_2^\prime + c_3^\prime)$};

@@

\node (d2) at (7,1) {$\mathbb{E}(M_2) \otimes \mathbb{E}(M_1)$};
\node (d3) at (7,2) {$\mathbb{E}(M_2 \otimes M_1)$};
\node (d4) at (7,-1) {$\mathbb{E}(M_1 \otimes M_2)$};
\node (d5) at (7,-2) {$\mathbb{E}(M_2 \otimes M_1)$};

@@

			\node (a2) at (-4,1) {$c_2+c_1$};
			\node (b2) at (0.5,1) {$R(d_2)+R(d_1)$};
			\node (c2) at (5,1) {$c_2^\prime+c_1^\prime$};
                                \node (a3) at (-4,2) {$c_2+c_1$};
			\node (b3) at (0.5,2) {$R(d_2+d_1)$};
			\node (c3) at (5,2) {$c_2^\prime + c_1^\prime$};
                                \node (a5) at (-4,-1) {$c_1+c_2$};
			\node (b5) at (0.5,-1) {$R(d_1+d_2)$};
			\node (c5) at (5,-1) {$c_1^\prime+c_2^\prime$};
                                \node (a6) at (-4,-2) {$c_2+c_1$};
			\node (b6) at (0.5,-2) {$R(d_2+d_1)$};
			\node (c6) at (5,-2) {$c_2^\prime + c_1^\prime$};

@@

(C) edge node[above]{$R(o)$} (B);

@@

\node (B) at (1.5,0) {$d$};
\node (C) at (3,0) {$L(c_2)$};
(A) edge node[above]{$\tau_{R(d)}L(R(i))$} (B)
(C) edge node[above]{$\tau_{R(d)}L(R(o))$} (B);

@@

(A) edge node[above]{$I$} (B)
(C) edge node[above]{$O$} (B);

@@

(A) edge node[above]{$\tau_c L(I)$} (B)
(C) edge node[above]{$\tau_c L(O)$} (B);

@@

(C) edge node[above]{$R(\tau_c)O$} (B);

@@

@@

@@

(C) edge node[above]{$R(o)$} (B);

@@

\node (B) at (1,0) {$N$};

@@

\node (D) at (3,0) {$M \in F(N)$};

@@

\node (E) at (4,0) {$M^\prime$};

@@

(D) edge node[above]{$i_2$} (E)
(F) edge node[above]{$o_2$} (E);
